FAIR fission track analysis with geochron@home

### 2025-10-06 geochron@home/manuscript/paper.tex
Fixed spelling

geochron@home was written in Python and Javascript. Its code is freely
available for inspection and modification, allowing users to set up
their own geochron@home server. Alternatively, users who would like to
upload data to the archive, but do not have the facilities to set up
their own server, may use the server at University College London free
of charge. The archive accepts image stacks acquired on any type of
digital microscope, and accomodates fission track data (counts and
length measurements) from external fission track analysis suites such
as Fission Track Studio and Track\emph{Flow}.\medskip

>>>>

geochron@home was written in Python and Javascript. Its code is freely
available for inspection and modification, allowing users to set up
their own geochron@home server. Alternatively, users who would like to
upload data to the archive, but do not have the facilities to set up
their own server, may use the server at University College London free
of charge. The archive accepts image stacks acquired on any type of
digital microscope, and accommodates fission track data (counts and
length measurements) from external fission track analysis suites such
as Fission Track Studio and Track\emph{Flow}.\medskip
